---
title: 'leaRning out loud: `r emo::ji_glue(":film_projector:")` slides from EARL Boston'
author: Mara Averick
date: '2017-11-05'
slug: learning-out-loud-slides-from-earl-boston
categories: []
tags:
  - events
  - slides
banner: "banners/earl_intro_slide.png"
images: ["banners/earl_intro_slide.png"]
description: 'I gave a talk at EARL Boston, and managed not to die! `r emo::ji_glue(":dizzy_face:")` Here are the slides from said non-fatal event for your enjoyment...'
---

`r emo::ji_glue(":tada:")` I gave a talk at [EARL Boston](https://earlconf.com/boston/), and somehow managed not to die! `r emo::ji_glue(":dizzy_face:")`

Couldn't make it? Here are the slides from the aforementioned, non-fatal event for your enjoyment. They likely won't make too much sense on their own, and I plan on doing a proper write-up at some point. But, until that time comes...

```{r, echo = FALSE}
blogdown::shortcode("speakerdeck", "738f4e63f3794cd48d5c05c103ac5a6f")
```

You can also catch a high(er)-resolution version of these same slides at: `r emo::ji_glue(" :link:")` <https://bit.ly/mara-earl>.

Questions? Comments? Snide remarks? Chirp my way `r emo::ji("bird")` [\@dataandme](https://twitter.com/dataandme).


#### Post Script

For the `r emo::ji_glue(":camera:")` POIDH crowd, here's proof positive (or some very excellent Photoshop work) from Angela Li (aka [\@CivicAngela](https://twitter.com/CivicAngela)).

```{r, echo = FALSE}
blogdown::shortcode("tweet", "926440586609135618")
```

