---
title: "😸 purrr-ty posts"
author: Mara Averick
date: '2017-09-26'
slug: purrr-ty-posts
categories: []
tags:
  - purrr
  - resources
  - R
  - roundups
banner: "banners/purrr_apply_cheatsheet_rstudio.png"
images: ["banners/purrr_apply_cheatsheet_rstudio.png"]
description: "Now that 😻 purrr has a shiny new cheat sheet, it seemed like a fitting tribute to give the package its own tweet roundup..."
---

Updated: `r emo::ji("calendar")` 2018-02-16.


### `r emo::ji("tada")``r emo::ji("cat")`&nbsp; purrr-tiest cheat sheet

Purrr royal decree (ok, I'll stop with the `r emo::ji("cat")` &nbsp;puns now), the [`purrr`](http://purrr.tidyverse.org/) `r emo::ji("package")` &nbsp;now has its very own official [RStudio cheat sheet](https://www.rstudio.com/resources/cheatsheets/): [**_Apply Functions Cheat Sheet_**](https://github.com/rstudio/cheatsheets/blob/master/purrr.pdf)

 >  The `purrr` package makes it easy to work with lists and functions. This cheatsheet will remind you how to manipulate lists with purrr as well as how to apply functions iteratively to each element of a list or vector. The back of the cheatsheet explains how to work with list-columns. With list columns, you can use a simple data frame to organize any collection of objects in R.

So, I thought we'd celebrate with a bit of a `purrr` `r emo::ji("bird")` &nbsp;tweet roundup:

### [Iteration of functions with purrr](http://perso.ens-lyon.fr/lise.vaudor/iterer-des-fonctions-avec-purrr/) by Lise Vaudor

```{r, echo = FALSE}
blogdown::shortcode("tweet", "963537570654310400")
```

### [purrr tutorial: lessons and examples](https://jennybc.github.io/purrr-tutorial/bk00_vectors-and-lists.html) by Jenny Bryan

```{r echo=FALSE}
blogdown::shortcode("tweet", "901627584651382785")
```

### [Labeling Data with purrr](http://www.json.blog/2017/03/labeling-data-with-purrr/) by Jason Becker

```{r echo=FALSE}
blogdown::shortcode("tweet", "840036799254790144")
```

### [Measuring Gobbledygook](https://juliasilge.com/blog/gobbledygook/) by Julia Silge

```{r echo=FALSE}
blogdown::shortcode("tweet", "802210752060936192")
```

### [Use quick formula functions in `purrr::map` (+ base vs tidtyverse idiom comparisons/examples)](https://rud.is/b/2016/07/26/use-quick-formula-functions-in-purrrmap-base-vs-tidtyverse-idiom-comparisonsexamples/) by Bob Rudis

```{r echo=FALSE}
blogdown::shortcode("tweet", "807348358746689540")
```

### [Make ggplot2 purrr](http://www.brodrigues.co/blog/2017-03-29-make-ggplot2-purrr/) by Bruno Rodrigues

```{r echo=FALSE}
blogdown::shortcode("tweet", "847195919019839493")
```

### [It's lists all the way down](http://www.brodrigues.co/blog/2018-01-03-lists_all_the_way/) by Bruno Rodrigues

```{r, echo = FALSE}
blogdown::shortcode("tweet", "948977872974368768")
```

There's also [**It's lists all the way down, part 2: We need to go deeper**](http://www.brodrigues.co/blog/2018-01-05-lists_all_the_way2/).

```{r, echo = FALSE}
blogdown::shortcode("tweet", "949642221745332224")
```

### [Putting square pegs in round holes: Using list-cols in your dataframe](https://speakerdeck.com/jennybc/putting-square-pegs-in-round-holes-using-list-cols-in-your-dataframe) by Jenny Bryan

```{r echo=FALSE}
blogdown::shortcode("tweet", "907063420515647490")
```

### [Managing many models with R](Managing many models with R) by Hadley Wickham

```{r echo=FALSE}
blogdown::shortcode("tweet", "802150368784379904")
```

### [The Many-Faced Future](http://www.jottr.org/2017/06/the-many-faced-future.html) by Henrik Bengtsson

```{r echo=FALSE}
blogdown::shortcode("tweet", "872136513844375553")
```

### [U.S. Drought Animations with the “Witch’s Brew” (purrr + broom + magick)](https://rud.is/b/2016/07/27/u-s-drought-animations-with-the-witchs-brew-purrr-broom-magick/) by Bob Rudis

```{r echo=FALSE}
blogdown::shortcode("tweet", "758735295952990209")
```

### [purrr workshop](https://www.dropbox.com/sh/062xjv35izc2a92/AAAnC-nzToR1rPekDZipRJSLa?dl=0) by Charlotte Wickham

```{r echo=FALSE}
blogdown::shortcode("tweet", "825041246850793473")
```

### [Pur(r)ify Your Carets](http://rsangole.netlify.com/post/pur-r-ify-your-carets/) by Rahul Sangole

```{r echo=FALSE}
blogdown::shortcode("tweet", "912788254692388864")
```

### [PURRRty PowerPoint with R](http://lenkiefer.com/2017/09/27/use-purrr/) by Len Kiefer

There's also [Purrrtier PowerPoint with R](http://lenkiefer.com/2017/10/21/purrrtier-powerpoint-with-r/), which covers the use of [`rvg`](https://github.com/davidgohel/rvg) for vector graphics.

```{r, echo = FALSE}
blogdown::shortcode("tweet", "913750757173800960")
```

### [A Crazy Little Thing Called {purrr} - Part 1 : Web Mining](http://colinfay.me/purrr-web-mining/) by Colin Fay

```{r, echo = FALSE}
blogdown::shortcode("tweet", "934619979680567296")
```

Now with part two: [**A Crazy Little Thing Called {purrr} - Part 2 : Text Wrangling**](http://colinfay.me/purrr-text-wrangling/)

```{r, echo = FALSE}
blogdown::shortcode("tweet", "936358492499251202")
```

Part three (which, apparently, I neglected to tweet): [**A Crazy Little Thing Called {purrr} - Part 3 : Setting NA**](http://colinfay.me/purrr-set-na/)

Part four: [**A Crazy Little Thing Called {purrr} - Part 4: mappers**](http://colinfay.me/purrr-mappers/)

```{r, echo = FALSE}
blogdown::shortcode("tweet", "940780583705366528")
```

Part five: [**A Crazy Little Thing Called {purrr} - Part 5: code optimization**](http://colinfay.me/purrr-code-optim/)

```{r, echo = FALSE}
blogdown::shortcode("tweet", "944568785540997120")
```

And part six: [**A Crazy Little Thing Called {purrr} - Part 6 : doing statistics**](http://colinfay.me/purrr-statistics/)

```{r, echo = FALSE}
blogdown::shortcode("tweet", "946467289892884480")
```

### [Reproducible Shiny App Development with Modules](https://www.blog.cultureofinsight.com/2018/01/reproducible-shiny-app-development-with-modules/) by Paul Campbell

```{r, echo = FALSE}
blogdown::shortcode("tweet", "949404399058776069")
```

### [Making many added variable plots with purrr and ggplot2](https://aosmith.rbind.io/2018/01/31/added-variable-plots/) by Ariel Muldoon

```{r, echo = FALSE}
blogdown::shortcode("tweet", "963611034022969345")
```

### `purrr`-fection?

This is a far cry from an exhaustive collection. If you've written something you think belongs here, send me a tweet `r emo::ji("bird")` &nbsp;([\@dataandme](https://twitter.com/dataandme)), or leave a comment. Blogging isn't exactly the best format for updated lists, but I'm hoping to cook up a better method soon!
