---
title: '2017 - A `r emo::ji_glue(":bird::heart:")` year in review'
author: Mara Averick
date: '2017-12-20'
slug: 2017-a-year-in-review
categories: []
tags:
  - R
  - resources
banner: "banners/2017_tweet_year.png"
images: ["banners/2017_tweet_year.png"]
description: 'Some twitter-follower favourites from each  `r emo::ji_glue(":calendar:")` month of 2017, featuring: R, Python, visualization, interactives, and other assorted items of interest along the way...'
---

I have no words of wisdom when it comes to summing up 2017. `r emo::ji_glue(":speak_no_evil:")` So, I guess I'll let some algorithm do the talking.[^1] `r emo::ji_glue(":robot::speech_balloon:")` Behold `r emo::ji_glue(":raised_hands:")`: two _Top Tweets_ for each month (according to [Twitter analytics](https://analytics.twitter.com)), some more R-related than others.

## January `r emo::ji_glue(":confetti_ball:")`

### [RStudio IDE Easy Tricks You Might've Missed](https://rviews.rstudio.com/2016/11/11/easy-tricks-you-mightve-missed/) by Sean Lopp

```{r, echo = FALSE}
blogdown::shortcode("tweet", "823366906551865344")
```

### [Data Visualisation Does Political Things](https://static1.squarespace.com/static/55ca3eafe4b05bb65abd54ff/t/574865601bbee06999548a9b/1464362348307/387+Boehnert.pdf) by Joanna Boehnert 

```{r, echo = FALSE}
blogdown::shortcode("tweet", "816732438005219328")
```

## February `r emo::ji_glue(":snowflake:")`

### [Data Transformation Cheat Sheet](https://www.rstudio.com/resources/cheatsheets/) via RStudio

```{r, echo = FALSE}
blogdown::shortcode("tweet", "835977000720470017")
```

### [Probability Cheatsheet v2.0](http://www.wzchen.com/probability-cheatsheet) by Joe Blitzstein and William Chen

```{r, echo = FALSE}
blogdown::shortcode("tweet", "829053628719706113")
```

## March `r emo::ji_glue(":wind_face:")`

### [DiagrammeR](https://rich-iannone.github.io/DiagrammeR/) by Richard Iannone

```{r, echo = FALSE}
blogdown::shortcode("tweet", "843534070873296897")
```

### [NHL shots analysis using Plotly shapes](https://moderndata.plot.ly/nhl-shots-analysis-using-plotly-shapes/)  by Pravendra Singh

```{r, echo = FALSE}
blogdown::shortcode("tweet", "837388642448474114")
```

## April `r emo::ji_glue(":umbrella:")`

### [A Compendium of Clean Graphs in R Version 2.0](http://shinyapps.org/apps/RGraphCompendium/index.php) by Eric-Jan Wagenmakers and Quentin F. Gronau

```{r, echo = FALSE}
blogdown::shortcode("tweet", "847994181800923136")
```

### [Conditional probability: A Visual explanation](http://setosa.io/conditional/) by Victor Powell

```{r, echo = FALSE}
blogdown::shortcode("tweet", "851182192772435968")
```

## May `r emo::ji_glue(":cherry_blossom:")`

### [Apply Functions Cheat Sheet](https://www.rstudio.com/resources/cheatsheets/) via RStudio

```{r, echo = FALSE}
blogdown::shortcode("tweet", "859952990173757441")
```

### [Every Color Of Cardigan Mister Rogers Wore From 1979-2001](https://www.theawl.com/2017/05/every-color-of-cardigan-mister-rogers-wore-from-1979-2001/) by Owen Phillips

```{r, echo = FALSE}
blogdown::shortcode("tweet", "866640293852057602")
```

## June `r emo::ji_glue(":graduation_cap:")`

### [skimr: A frictionless, pipeable approach to dealing with summary statistics](https://github.com/ropenscilabs/skimr) via rOpenSci

```{r, echo = FALSE}
blogdown::shortcode("tweet", "870686970841776129")
```

### [29 common beginner Python errors on one page](https://pythonforbiologists.com/29-common-beginner-errors-on-one-page/) via Python for Biologists

```{r, echo = FALSE}
blogdown::shortcode("tweet", "873650237994348545")
```

## July `r emo::ji_glue(":sunglasses:")`

### [Introducing learnr](https://blog.rstudio.com/2017/07/11/introducing-learnr/) by Garrett Grolemund

```{r, echo = FALSE}
blogdown::shortcode("tweet", "884884260963921920")
```

### [You Say Data, I Say System](https://hackernoon.com/you-say-data-i-say-system-54e84aa7a421) by Jer Thorp

```{r, echo = FALSE}
blogdown::shortcode("tweet", "886217300705239040")
```

## August `r emo::ji_glue(":sweat_smile:")`

### [Basic Regular Expressions in R Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2016/09/RegExCheatsheet.pdf) by Ian Kopacka

```{r, echo = FALSE}
blogdown::shortcode("tweet", "893905958107308033")
```

### [Visualization Analysis & Design](http://www.cs.ubc.ca/~tmm/talks.html) by Tamara Munzer

```{r, echo = FALSE}
blogdown::shortcode("tweet", "901878507357302784")
```

## September `r emo::ji_glue(":fallen_leaf:")`

### [Network visualization with R](http://kateto.net/network-visualization) by Katya Ognyanova

```{r, echo = FALSE}
blogdown::shortcode("tweet", "904691129488113664")
```

### [Data Import Cheat Sheet](https://www.rstudio.com/resources/cheatsheets/) via RStudio

```{r, echo = FALSE}
blogdown::shortcode("tweet", "904389043986817026")
```

## October `r emo::ji_glue(":jack_o_lantern:")`

### [Introduction to gghighlight](https://yutani.rbind.io/post/2017-10-06-gghighlight/) by Hiroaki Yutani

```{r, echo = FALSE}
blogdown::shortcode("tweet", "917435038186266624")
```

### [You draw the chart: How has life changed in 60 years?](http://www.bbc.com/news/uk-41685693) by Wesley Stephenson

```{r, echo = FALSE}
blogdown::shortcode("tweet", "923535196246499328")
```

## November `r emo::ji_glue(":turkey:")`

### [Working with Play-by-Play Sports Data: Using SQL & R](http://curleylab.psych.columbia.edu/playbyplay/) by James Curley

```{r, echo = FALSE}
blogdown::shortcode("tweet", "926857078400053249")
```

### [tidyverse 1.2.0](https://www.tidyverse.org/articles/2017/11/tidyverse_1.2.0/)

```{r, echo = FALSE}
blogdown::shortcode("tweet", "928276461991223296")
```

## December `r emo::ji_glue(":christmas_tree:")`

### [Visualizing text data with ggplot2](https://github.com/ColinFay/conf/blob/master/2017-11-budapest/fay_colin_text_data_ggplot2.pdf) by Colin Fay

```{r, echo = FALSE}
blogdown::shortcode("tweet", "938468603539705856")
```

### [Data Visualization for Social Science: A practical introduction with R and ggplot2](http://socviz.co/index.html) by Kieran Healy

```{r, echo = FALSE}
blogdown::shortcode("tweet", "938968652040241152")
```

[^1]: With some mild editorializing to include at least a _few_ useful things along the way.
