---
title: base-shaming and the fetishisation of tidy data
author: Mara Averick
date: '2017-09-02'
draft: TRUE
slug: base-shaming-fetishisation-of-tidy-data
categories: []
tags:
  - R
  - tidyverse
  - STS
---

Back in 2016, Nathan Yau (author/curator of <flowingdata.com>) wrote a post on his blog, [**Comparing ggplot2 and R Base Graphics**](https://flowingdata.com/2016/03/22/comparing-ggplot2-and-r-base-graphics/). His conclusion is unsurprising (when in doubt, _it depends_ is almost always a legitimate answer):

> Should _you_ use ggplot2 or base graphics? Tough call.

The impetus for the post, as he described it, seemed somewhat more value-laden.

> However, last month, Jeff Leek explained [why he purposely avoids ggplot2](https://simplystatistics.org/2016/02/11/why-i-dont-use-ggplot2/). Then David Robinson rebutted with [why ggplot2 is superior to R’s lowly base graphics](http://varianceexplained.org/r/why-I-use-ggplot2/).

```{r echo=FALSE}
blogdown::shortcode("tweet", "712263204349423617")
```

When I tweeted that link (I was so young and innocent back in March of 2016), I guess I didn't fully appreciate that the tensions among the parties (_actor networks_, if you will) went beyond good-natured banter.

```{r echo=FALSE}
blogdown::shortcode("tweet", "903001691598897152")
```


I _certainly_ didn't think it indicated anything nearing the magnitude of one of the great statistical "controversies" (for lack of a better word) of the past two centuries.[^Mcgrayne2012]

```{r echo=FALSE}
blogdown::shortcode("tweet", "903003120317325314")

blogdown::shortcode("tweet", "902933897587171329")
```


## `base` vs. `tidyverse`: a false dichotomy with real consequences?

```{r echo=FALSE}
blogdown::shortcode("tweet", "902910720165203968")
```


```{r echo=FALSE}
blogdown::shortcode("tweet", "902916684612239360")
```

[^Mcgrayne2012]: McGrayne, Sharon Bertsch. 2012. The Theory That Would Not Die: How Bayes’ Rule Cracked the Enigma Code, Hunted Down Russian Submarines, and Emerged Triumphant from Two Centuries of Controversy. Yale University Press.