---
title: 'Keeping up with blogdown `r emo::ji_glue(":star2:")`'
author: Mara Averick
date: '2017-10-07'
lastmod: '`r Sys.Date()`'
slug: keeping-up-with-blogdown
categories: []
tags:
  - blogdown
  - R
  - R Markdown
  - resources
  - roundups
banner: "banners/blogdown_banner_grid.jpg"
images: ["banners/blogdown_banner_grid.jpg"]
description: "A quick roundup of some of the many great blogdown resources out there to get you up and blogging in R Markdown."
---

_Updated: 2018-03-22_ 

I've loved [blogdown](https://github.com/rstudio/blogdown) `r emo::ji_glue(":package:")` for so long, that I was kind of shocked `r emo::ji_glue(":scream:")` when I saw [Yinui Xie](https://yihui.name/)'s post, [**Announcing blogdown: Create Websites with R Markdown**](https://blog.rstudio.com/2017/09/11/announcing-blogdown/), on the [RStudio blog](https://blog.rstudio.com/) just _last month_!

Have people really been living without the magic `r emo::ji_glue(":sparkles:")` of blogdown in their lives for so long?! If you are one of these people, then hopefully this post (which, _yes_, is really just a roundup of tweets) will inspire you to join in on the fun `r emo::ji_glue(":dancers:")`.

## `blogdown`: the definitive guide `r emo::ji_glue(":book:")`

Obviously I dig all the resources that will ensue, but I'd be remiss were I _not_ to point out that the bookdown book, [**_blogdown: Creating Websites with R Markdown_**](https://bookdown.org/yihui/blogdown/) by Yihui Xie, Amber Thomas, and Alison Presmanes Hill, is where it's at `r emo::ji_glue(":raised_hands:")`.

```{r, echo = FALSE}
blogdown::shortcode("tweet", "915200318455128065")
```

In addition to covering the how-to from start to finish, it's constantly being updated (last was `r emo::ji_glue(":date:")` 2018-02-12, as of this writing)-- so, it's a real go-to!

They've also added a minimal [blogdown demo site](https://blogdown-demo.rbind.io/about/), which is _incredibly_ helpful if you're just getting set up.

```{r, echo = FALSE}
blogdown::shortcode("tweet", "968954545715007489")
```

## Further blogdown resources abound `r emo::ji_glue(":heart_eyes:")`

### [Building a Blog with Blogdown and GitHub](https://tclavelle.github.io/blog/blogdown_github/) by Tyler Clavelle

```{r, echo = FALSE}
blogdown::shortcode("tweet", "914600098398658561")
```


### [Making a Website Using Blogdown, Hugo, and Github pages](https://proquestionasker.github.io/blog/2016/12/19/creatingsite/) by Amber Thomas

```{r, echo = FALSE}
blogdown::shortcode("tweet", "816119147830591488")
```


### [Up and running with blogdown](https://apreshill.rbind.io/post/up-and-running-with-blogdown/) by Alison Presmanes Hill

```{r, echo = FALSE}
blogdown::shortcode("tweet", "876787157070950401")
```

And a more recent variation on her talk:

```{r, echo = FALSE}
blogdown::shortcode("tweet", "941005303516102656")
```

### [Making Websites with R Markdown: A Sneak Peek of blogdown](https://slides.yihui.name/2017-rstudio-conf-blogdown-Yihui-Xie.html#1) by Yihui Xie

```{r, echo = FALSE}
blogdown::shortcode("tweet", "823893638589673473")
```


### [Blogdown tutorials (Parts 1 - 4)](http://notes.peter-baumgartner.net/tutorial/) by Peter Baumgartner

```{r, echo = FALSE}
blogdown::shortcode("tweet", "915579627338420224")
```


### [Building a Blogdown Site with Travis-CI](http://enpiar.com/2017/06/01/building-a-blogdown-site-with-travis-ci/) by Neal Richardson

```{r, echo = FALSE}
blogdown::shortcode("tweet", "916011630592450560")
```

### [Make Your Own Blog Using R](https://github.com/rladies/meetup-presentations_london/tree/master/2017-04-26_Make_your_own_blog) by Claudia Vitolo

```{r, echo = FALSE}
blogdown::shortcode("tweet", "862714432094433280")
```

### [Creating websites in R](http://www.emilyzabor.com/tutorials/rmarkdown_websites_tutorial.html) by Emily Zabor

```{r, echo = FALSE}
blogdown::shortcode("tweet", "975192324505563136")
```

### [Awesome blogdown: a curated list of blogs built using blogdown](https://github.com/sellorm/awesome-blogdown) by Mark Sellors

```{r, echo = FALSE}
blogdown::shortcode("tweet", "912395892409475072")
```

## Fin...for now `r emo::ji_glue(":grimacing:")`

There are a _ton_ of blogdown resources out there, many of which I haven't covered here (especially when it comes to moving from a specific platform _to_ blogdown, which could be a category unto itself). As always, tweet me ([\@dataandme](https://twitter.com/dataandme)) `r emo::ji("bird")`, or comment if you have questions and/or suggestions. Perhaps a second roundup will be in store for blogdown.

