---
title: 'Refind `r emo::ji_glue(":mag_right:")``r emo::ji_glue(":recycle:")`'
author: Mara Averick
date: '2017-10-27'
slug: refind
categories: []
tags:
  - wild-card
banner: 'banners/refind_banner-min.png'
images: ['banners/refind_banner-min.png']
description: 'This isn’t much in the way of a post, but (as tweeted earlier `r emo::ji_glue(":bird:")`), I’ve been digging refind of late...'
---

It's not much in the way of a post, but (as tweeted earlier `r emo::ji_glue(":point_down:")`), I've been digging [refind](https://refind.com/dataandme?invite=833f3aa88b) of late.[^1]

```{r, echo = FALSE}
blogdown::shortcode("tweet", "918091767244869633")
```

Yes, it's just another bookmarking tool— or discovery engine, or whatever it is the kids are calling things these days... The point is, it takes all the links from my tweets `r emo::ji_glue(":bird:")`, and puts them in a much more browsable format. You also get to avoid my side comments and emoji-annotation, which is `r emo::ji_glue(":thumbsup:")` or `r emo::ji_glue(":thumbsdown:")`, depending on whom you ask.

See? All the cards in the banner started out as tweets:

#### [A tidy text analysis of Rick and Morty](http://tamaszilagyi.com/blog/a-tidy-text-analysis-of-rick-and-morty/) by Tamas Szilagyi

```{r, echo = FALSE}
blogdown::shortcode("tweet", "917737120105680896")
```

#### [RStudio v1.1 Released](https://blog.rstudio.com/2017/10/09/rstudio-v1.1-released/) by Jonathan McPherson

```{r, echo = FALSE}
blogdown::shortcode("tweet", "917485189563117569")
```

#### [How I built a scraper to measure activity of MPs](http://www.maartenlambrechts.com/2016/10/03/how-i-built-a-scraper-to-measure-activity-of-mps.html) by Maarten Lambrechts

```{r, echo = FALSE}
blogdown::shortcode("tweet", "917461179211112448")
```

#### [An extensive tutorial of D3partitionR 0.2](https://antoineguillot.wordpress.com/2016/11/20/an-extensive-tutorial-of-d3partitionr-0-2/) by Antoine Guillot

```{r, echo = FALSE}
blogdown::shortcode("tweet", "917374619132354561")
```

Ah, the magic of Web APIs! `r emo::ji_glue(":sparkles:")` 

So, here's your formal [invitation](https://refind.com/dataandme?invite=833f3aa88b) `r emo::ji_glue(":scroll:")`, should you care to join in on the fun!

[^1]: Scout's honor `r emo::ji_glue(":hand:")`, I'm not in it for the billion imaginary coins, or whatever it is the claim to be giving away.
