---
title: 'Docker-izing your work in R `r emo::ji("whale")`'
author: Mara Averick
date: '2017-11-20'
lastmod: '`r Sys.Date()`'
slug: docker-izing-your-work-in-r
categories: []
tags:
  - R
  - rOpenSci
  - roundups
banner: "banners/nyan_docker_whale_gfycat.gif"
images: ["banners/nyan_docker_whale_gfycat.gif"]
description: 'A roundup of helpful guides to containerizing packages, docs, projects, and more by using Docker with R. `r emo::ji("package")`'
---

```{r include=FALSE}
library(emo)
```

_Updated: 2018-07-15_

I am decidedly a novice when it comes to any and all things Docker (which, 
incidentally, is why I've been reading these posts). But, since it's helpful for 
_me_ to have all of these resources together in one place, I thought I'd share 
the love around.[^nyanwhale]

### [R Docker turorial for reproducible research.](http://ropenscilabs.github.io/r-docker-tutorial/) via rOpenSci Labs

This is actually a series of *6* lessons put together at the 
rOpenSci unconf in 2016.

```{r, echo = FALSE}
blogdown::shortcode("tweet", "930633713876127744")
```

### [Docker for the UseR](https://github.com/noamross/nyhackr-docker-talk) by Noam Ross

```{r, echo = FALSE}
blogdown::shortcode("tweet", "1017077037146796032")
```

### [Enough Docker to be Dangerous](http://seankross.com/2017/09/17/Enough-Docker-to-be-Dangerous.html) by Sean Kross

```{r, echo = FALSE}
blogdown::shortcode("tweet", "911774443885797377")
```

### [liftr](https://liftr.me/) `r emo::ji("package")` by Nan Xiao

```{r, echo = FALSE}
blogdown::shortcode("tweet", "919548925287297024")
```

> liftr aims to solve the problem of _persistent reproducible reporting_. 
> To achieve this goal, it extends the R Markdown metadata format, 
> and uses Docker to containerize and render R Markdown documents.

### [Docker for R Package Development](http://www.jimhester.com/2017/10/13/docker/) by Jim Hester

```{r, echo = FALSE}
blogdown::shortcode("tweet", "918910727070601217")
```

### [An R-docker hello world example](https://www.symbolix.com.au/blog-main/r-docker-hello) via symbolix

```{r, echo = FALSE}
blogdown::shortcode("tweet", "910938183386484738")
```

### [How to get started with data science in containers](http://blog.kaggle.com/2016/02/05/how-to-get-started-with-data-science-in-containers/) by Jamie Hall

This post isn't R-specific, but that doesn't mean it's not useful!

```{r, echo = FALSE}
blogdown::shortcode("tweet", "696057282325561344")
```

### [Dockerized Shiny App development](http://tamaszilagyi.com/blog/dockerized-shiny-app-development/) by Tamas Szilagyi

```{r, echo = FALSE}
blogdown::shortcode("tweet", "954353292221575168")
```

### [stevedore: A docker client for R](https://richfitz.github.io/stevedore/) by Rich FitzJohn

```{r, echo = FALSE}
blogdown::shortcode("tweet", "935264570901442560")
```

### [Using RSelenium and Docker To Webscrape In R - Using The WHO Snake Database](https://callumgwtaylor.github.io/blog/2018/02/01/using-rselenium-and-docker-to-webscrape-in-r-using-the-who-snake-database/) by Callum Taylor

```{r, echo = FALSE}
blogdown::shortcode("tweet", "961074296515899393")
```

### [Dockerise and deploy your own R Archive Repo](https://rtask.thinkr.fr/blog/dockerise-and-deploy-your-own-r-archive-repo/) by Colin Fay

```{r, echo = FALSE}
blogdown::shortcode("tweet", "1004908127521828864")
```

### [Shipping Data Science Products with R and Docker](https://itsalocke.com/talks/post/shipping-r-with-docker/) by Steph Locke

```{r, echo = FALSE}
blogdown::shortcode("tweet", "1014846062568312835")
```

## Fin `r emo::ji("tada")`

Additions? Questions? Comments? Snide remarks? Feel free to tweet me [\@dataandme](https://twitter.com/dataandme) `r emo::ji("bird")`, and/or comment below!

[^nyanwhale]: Speaking of sharing love: cred for [Nyan Whale](https://gfycat.com/gifs/detail/PerfectHarshHoatzin) (i.e. the banner gif `r emo::ji("rainbow")`) goes to [Andrew Kennedy](https://www.youtube.com/watch?v=2c_rmqme6rc)!

