---
title: tidyeval resource roundup
author: Mara Averick
date: '2017-08-26'
lastmod: '`r Sys.Date()`'
slug: tidyeval-resource-roundup
categories: []
tags:
  - R
  - resources
  - tidyeval
  - tidyverse
  - roundups
banner: "banners/tidyeval_combo.png"
images: ["banners/tidyeval_combo.png"]
description: 'Updated `r emo::ji("calendar")` 2018-02-24. After posting a link to Edwin Thoen’s "Tidy evaluation most common actions," I was asked if there were other tidy eval resources I knew of. So, here are some of the tutorials  I’ve found and tweeted.'
---

_Updated: 2018-02-24_  

Though, naturally, the [Honorable Professor Doctor Sir Lord General Hadley Wickham](http://hadley.nz/)'s [**Programming with dplyr**](http://dplyr.tidyverse.org/articles/programming.html) article is the _ne plus ultra_ of getting oneself aquainted with the latest and greatest in [tidyeval programming recipes](http://dplyr.tidyverse.org/articles/programming.html#programming-recipes), [quoting](http://dplyr.tidyverse.org/articles/programming.html#quoting), and [quasiquotation](http://dplyr.tidyverse.org/articles/programming.html#quasiquotation); there _are_ some other resources out there.

After posting a link to [Edwin Thoen](https://edwinth.github.io)'s ⭐️ [**Tidy evaluation, most common actions**](https://edwinth.github.io/blog/dplyr-recipes/), I was asked if there were other `tidyeval` tutorials I knew of. And so, here are some resources I've found and tweeted.[^1]

```{r echo=FALSE}
blogdown::shortcode("tweet", "901429535266267136")
```

### [Tidy evaluation in 5 minutes](https://www.youtube.com/watch?v=nERXS3ssntw) by Hadley Wickham

```{r, echo = FALSE}
blogdown::shortcode("tweet", "963175175658397701")
```

### [Lesser known `dplyr` 0.7* tricks](http://www.brodrigues.co/blog/2017-06-19-dplyr-0-70-tutorial/) by Bruno Rodrigues

```{r echo=FALSE}
blogdown::shortcode('tweet', '881860624808128512')
```

### [Why I find tidyeval useful](http://www.brodrigues.co/blog/2017-08-27-why_tidyeval/) by Bruno Rodrigues

```{r echo=FALSE}
blogdown::shortcode("tweet", "902278898968170496")
```

### [Making Sense of `dplyr` 0.6](http://www.json.blog/2017/05/making-sense-of-dplyr-0.6/?utm_content=bufferb2c45&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer) by Jason Becker

```{r echo=FALSE}
blogdown::shortcode('tweet', '865975935245451264')
```

### [gentle non-standard evaluation in `dplyr` 0.6](https://alexpghayes.github.io/2017/gentle-non-standard-evaluation-in-dplyr-0-6/?utm_content=buffer3fc76&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer) by Alex Hayes

```{r echo=FALSE}
blogdown::shortcode('tweet', '866364480212611072')
```

### [Excluding Rows](https://romain.rbind.io/blog/2017/07/01/excluding-rows/?utm_content=bufferc1336&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer) by Romain François

```{r echo=FALSE}
blogdown::shortcode('tweet', '881584765073227780')
```

### [`set_na_where()`: a nonstandard evaluation use case](https://tjmahr.github.io/set-na-where-nonstandard-evaluation-use-case/?utm_content=buffer2d7a9&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer) by Tristan Mahr

```{r echo=FALSE}
blogdown::shortcode('tweet', '899341779962605568')
```

### [Down the rabbit hole with tidy eval — Part 1](http://colinfay.me/tidyeval-1/) by Colin Fay

```{r echo=FALSE}
blogdown::shortcode("tweet", "902214722572996612")
```

### [Non-standard evaluation, how tidy eval builds on base R](https://edwinth.github.io/blog/nse/) by Edwin Thoen

```{r echo=FALSE}
blogdown::shortcode("tweet", "906925770538455040")
```

### [My First Steps into The World of Tidy Eval](www.onceupondata.com/2017/08/12/my-first-steps-into-the-world-of-tidyeval/) by Omayma
```{r echo=FALSE}
blogdown::shortcode("tweet", "909126265923391488")
```

### [`dplyr 0.7.0`: tidyeval / programming with dplyr](https://github.com/rladies/meetup-presentations_boston/blob/master/Boston_20170817_tidyeval_ppt.pdf) by Marianna Foos

```{r echo=FALSE}
blogdown::shortcode("tweet", "912025352666583040")
```

### [Do it With Quasi-Quotation](http://blog.jalsalam.com/posts/2017/quasi-quotation-applications/) by Jameel Alsalam

```{r, echo = FALSE}
blogdown::shortcode("tweet", "935344760029671424")
```

### [Theory free tidyeval](https://www.johnmackintosh.com/2018-02-19-theory-free-tidyeval/) by John MacKintosh

```{r, echo = FALSE}
blogdown::shortcode("tweet", "966799020281692161")
```

### [filter with context](https://purrple.cat/blog/2017/06/28/filter-with-context/) by Romain François

```{r, echo = FALSE}
blogdown::shortcode("tweet", "968973417197309954")
```

## `r emo::ji_glue(":film_projector:")` [Tidy Evaluation](https://schd.ws/hosted_files/user2017/43/tidyeval-user.pdf) by Lionel Henry and Hadley Wickham

_n.b. these are likely not as up-to-date as [**Programming with dplyr**](http://dplyr.tidyverse.org/articles/programming.html), but I like the visuals— so, they're here_

```{r, echo = FALSE}
blogdown::shortcode("tweet", "919311107357069316")
```

### Ta-da 🎉

If you've written and/or found more examples that you think would be helpful to have in here, by all means give me a shout! Actually, a tweet 🐦 ([\@dataandme](https://twitter.com/dataandme)) would probably be best...which, I know, is totally tragic.

[^1]: Yes, I'm just leaving them as tweets, because they already have author names, and screenshots and...y'know what? If you don't want them in tweet form, go write your own post! (I'm kidding, of course 😉)

