---
title: RegEx resources
author: Mara Averick
date: '2017-09-21'
lastmod: '`r Sys.Date()`'
slug: regex-resources
categories: []
tags:
  - R
  - RegEx
  - resources
  - stringr
  - roundups
banner: "banners/regex_tweets.jpg"
images: ["banners/regex_tweets.jpg"]
description: "At some point in your computing life, you're gonna need to get down with regular expressions. So, here's a roundup of some Regex-related resources (R-specific or otherwise) I've found handy."
---

Updated: `r emo::ji("calendar")` 2017-10-27.

Regular Expressions, RegEx, regexps-- call them what you like, but no matter how you slice it, they're useful af. After all, data spelunking is all about patterns, and that's precisely what regexps are for: (wo)manhandling patterns in strings. Good Sirs Wickham and Grolemund, in their masterful tome, [r4ds](http://r4ds.had.co.nz/strings.html#matching-patterns-with-regular-expressions), describe them thusly:

 > They [regexps] take a little while to get your head around, but once you understand them, you’ll find them extremely useful.[^r4dsregex]
 
There are helpful string-related R packages `r emo::ji("package")`, [`stringr`](http://stringr.tidyverse.org/) (which is built on top of the more comprehensive [`stringi`](https://github.com/gagolews/stringi) package) comes to mind. But, at some point in your computing life, you're gonna need to get down with regular expressions.

And so, here's a collection of some of the Regex-related links I've tweeted `r emo::ji("bird")`:

### [Basic Regular Expressions in R Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2016/09/RegExCheatsheet.pdf) by Ian Kopacka

```{r regex_cheatsheet, echo=FALSE}
blogdown::shortcode("tweet", "852869552191012865")
```

### [strings and regular expressions](http://perso.ens-lyon.fr/lise.vaudor/strings-et-expressions-regulieres/) by Lise Vaudor

```{r lvaudor_regexps, echo=FALSE}
blogdown::shortcode("tweet", "904453200157302784")
```

### [Quick Guide to Regex in R](https://gormanalysis.com/quick-guide-to-regex-in-r) by Ben Gorman

```{r gorman_quick_guide, echo=FALSE}
blogdown::shortcode("tweet", "809596167449432066")
```

### [An Introduction to stringr and Regular Expressions](https://rstudio-pubs-static.s3.amazonaws.com/180610_d3764c43f1e54692b7e84d21ec94772a.html#1) by Brian Espinoza

```{r intro_stringr_regex_slides, echo=FALSE}
blogdown::shortcode("tweet", "890755949744586753")
```

### [qdapRegex](https://github.com/trinker/qdapRegex) `r emo::ji("package")` by Tyler Rinker

```{r qdapRegex, echo=FALSE}
blogdown::shortcode("tweet", "874250442812907521")
```

### [RegexOne](https://regexone.com/) simple, interactive exercises

```{r regexone, echo=FALSE}
blogdown::shortcode("tweet", "799251262344572928")
```

### [Regular expressions in `swirl`](http://joncalder.co.za/Regular_Expressions/) by Jon Calder

```{r, echo = FALSE}
blogdown::shortcode("tweet", "913875288605577216")
```

### [Awesome new `stringr` cheat sheet](https://www.rstudio.com/resources/cheatsheets/) from RStudio

```{r, echo = FALSE}
blogdown::shortcode("tweet", "923969983708835842")
```

#### Tada `r emo::ji("tada")`

As always, by all means let me know if you've written something you think I should add: chirp my way  (`r emo::ji("bird")` [\@dataandme](https://twitter.com/dataandme)), comment-- you know the drill.

[^r4dsregex]: Wickham, Hadley and Garrett Grolemund. 2016. _R for Data Science_. Sebastopol: O'Reilly Media. Web. <http://r4ds.had.co.nz/strings.html#matching-patterns-with-regular-expressions> 20 September, 2017. 

