---
title: 'ggraph all grown up `r emo::ji("giraffe")`'
author: Mara Averick
date: '2018-02-23'
draft: TRUE
slug: ggraph-all-grown-up
categories: []
tags:
  - R
  - visualization
  - data viz
  - ggraph
  - roundups
banner: "banners/data-imaginist.gif"
images: ["banners/data-imaginist.gif"]
description: 'A CRANniversary `r emo::ji("cake")` roundup of some of my favourite posts featuring ggraph, the network visualization `r emo::ji("package")` by Thomas Lin Pedersen.'
---

Thomas Lin Pedersen (known aliases: [\@thomasp85](https://twitter.com/thomasp85), [data imaginist](https://www.data-imaginist.com/)) has quite an array of [cool packages](https://github.com/thomasp85), all of which you should check out. However, in celebration its **CRANniversary** `r emo::ji("balloon")` I thought [**ggraph**](https://github.com/thomasp85/ggraph) deserved a roundup post of its own.[^1]

## Dispatches from a proud papa `r emo::ji("dad")`

### [ggraph: A grammar of graphics for relational data](https://github.com/thomasp85/ggraph)

_The repo from whence it sprang..._

```{r, echo = FALSE}
blogdown::shortcode("tweet", "777130491287928832")
```

### [Data Driven Logo Design with ggraph and gtable](https://www.data-imaginist.com/2016/data-driven-logo/)

_Source of the animated logo serving as the banner for this post._

```{r, echo = FALSE}
blogdown::shortcode("tweet", "785301087578419200")
```

### [Announcing ggraph: A grammar of graphics for relational data](https://www.data-imaginist.com/2017/announcing-ggraph/)

```{r, echo = FALSE}
blogdown::shortcode("tweet", "835188089911922688")
```

### [Introduction to ggraph: Layouts](https://www.data-imaginist.com/2017/ggraph-introduction-layouts/)

```{r, echo = FALSE}
blogdown::shortcode("tweet", "830068094227902464")
```

### [Introduction to ggraph: Nodes](https://www.data-imaginist.com/2017/ggraph-introduction-nodes/)

```{r, echo = FALSE}
blogdown::shortcode("tweet", "950927436396613632")
```

### [Introduction to ggraph: Edges](https://www.data-imaginist.com/2017/ggraph-introduction-edges/)

```{r, echo = FALSE}
blogdown::shortcode("tweet", "832677509258846213")
```

## Applied posts from fellow fans `r emo::ji("memo")`

### [A Gentle Introduction to Network Visualisation](http://colinfay.me/back-budapest/) by Colin Fay

```{r, echo = FALSE}
blogdown::shortcode("tweet", "932696587398275072")
```

### [How to create correlation network plots with corrr and ggraph](https://drsimonj.svbtle.com/how-to-create-correlation-network-plots-with-corrr-and-ggraph) by Simon Jackson

```{r, echo = FALSE}
blogdown::shortcode("tweet", "836577246945099776")
```

### [Plotting trees from Random Forest models with ggraph](https://shiring.github.io/machine_learning/2017/03/16/rf_plot_ggraph) by Shirin Glander

```{r, echo = FALSE}
blogdown::shortcode("tweet", "842722809709256704")
```

### [Holy ifelse() statements Batman!](http://austinwehrwein.com/data-visualization/plotting-batman-villains-ggraph/) by Austin Wehrwein

```{r, echo = FALSE}
blogdown::shortcode("tweet", "952903820945870849")
```

## Tada! `r emo::ji_glue(":tada:")`

As always, I'm sure there are many more posts out there I've missed. If there's something you'd like to see added, send me a tweet `r emo::ji("bird")` &nbsp;([\@dataandme](https://twitter.com/dataandme)).

[^1]: And by "post" I do, of course, really mean collection of tweets.
