---
title: Harvest of rvest
author: Mara Averick
date: '2018-03-29'
lastmod: '`r Sys.Date()`'
draft: TRUE
slug: harvest-of-rvest
categories: []
tags:
  - rvest
  - R
  - roundups
banner: ""
images: [""]
description: 'rvest `r emo::ji("package")` posts'
---

### [Extracting data from the web APIs and beyond](https://github.com/ropensci/user2016-tutorial) by Karthik Ram, Garrett Grolemund and Scott Chamberlain

```{r, echo = FALSE}
blogdown::shortcode("tweet", "799013459291684864")
```

### [Scraping NBA Stats From The Web](http://kevinfw.com/post/web-scraping-with-r/) by Kevin Wong

```{r, echo = FALSE}
blogdown::shortcode("tweet", "836692091522727937")
```

### [Guardian Film Reviews](https://www.mytinyshinys.com/2017/10/07/guardian-film-reviews/) by Andrew Clark

```{r, echo = FALSE}
blogdown::shortcode("tweet", "917861579730731010")
```

### [Auto Emojis](http://giorasimchoni.com/2017/07/02/2017-07-02-emojis-diy/) by Giora Simchoni

```{r, echo = FALSE}
blogdown::shortcode("tweet", "915260669926178816")
```

### [Who's on everyone's 2017 "hit list"?](https://suzanbaert.netlify.com/2018/01/2017radiohitlist/) by Suzan Baert

```{r, echo = FALSE}
blogdown::shortcode("tweet", "949728783875166208")
```

### [Scraping CRAN with rvest](https://juliasilge.com/blog/scraping-cran/) by Julia Silge

```{r, echo = FALSE}
blogdown::shortcode("tweet", "839838692881620994")
```

### [Extracting notable deaths from Wikipedia](http://www.masalmon.eu/2017/02/12/wikideaths3_scraping/) by Maëlle Salmon

```{r, echo = FALSE}
blogdown::shortcode("tweet", "831564310358929408")
```

### [Diving Into Dynamic Website Content with splashr](https://rud.is/b/2017/02/09/diving-into-dynamic-website-content-with-splashr/) by Bob Rudis

```{r, echo = FALSE}
blogdown::shortcode("tweet", "831926662753374208")
```

### [NBA Draft Scraping, the R Way](http://asbcllc.com/blog/2015/september/nba_draft_scraping_the_r_way/index.html) by Alex Bresler

```{r, echo = FALSE}
blogdown::shortcode("tweet", "775154274439430144")
```

### [The Cost of True Love](https://rud.is/b/2017/12/05/the-cost-of-true-love-a-k-a-the-tidy-and-expensive-twelve-days-of-christmas/) by Bob Rudis

```{r, echo = FALSE}
blogdown::shortcode("tweet", "938408253939159040")
```

