---
title: The transaction of talks
author: Mara Averick
date: '2019-08-07'
slug: 2019-08-the-transaction-of-talks
categories: []
tags:
  - wild-card
banner: ''
description: ''
images: []
menu: ''
---

<!--more-->

When someone invites you to speak for 15 minutes, they are asking for more than 15 minutes of your time. In fact, Woodrow Wilson once suggested that the duration of time needed for preparation is inversely proportionate to that for which you are to speak:

> If I am to speak ten minutes, I need a week for preparation; if fifteen minutes, three days; if half an hour, two days; if an hour, I am ready now. [^qi]


```{r libs, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(scales)
```


```{r wilson_prep, echo=FALSE}
mins_needed <- tibble::tribble(
                 ~duration, ~preparation,
                        10,        10080,
                        15,         4320,
                        30,         2880,
                        60,            0
                 )

mins_needed <- mins_needed %>%
  mutate(desc = c("1 week", "3 days", "2 days", ""))

ggplot(data = mins_needed, aes(x = duration, y = preparation, label = desc)) +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = desc),
                            family = "Roboto Condensed",
                            segment.alpha = 0.4,
                            nudge_x = 5,
                            ) +
  scale_y_continuous(labels = comma) +
  hrbrthemes::theme_ipsum_rc() +
  labs(title = "Woodrow Wilson's speech-duration vs prep time needed",
       subtitle = "Time needed to prepare by length of talk (in mins)",
      x = "duration",
      y = "preparation")

```

I don't think my distribution of time needed would look like Wilson's. I certainly wouldn't feel ready to give an hour-long talk right now. But the point is that speaking requires quite a bit of time.[^mayvary] 

__It's *definitely* worth it.__[^erob] I am incredibly grateful for the opportunities I've had to speak, and those who have helped and encouraged me along the way.

At the same time, talks and posters are a huge part of what conferences are made of -- they're "the show." So, it should basically be mutually beneficial. 

All of this was inspired by the [Call for Speakers](https://womeninanalytics.com/call-for-speakers/) for [Women in Analytics 2020](https://womeninanalytics.com/call-for-speakers/), which includes a list of _Benefits of Speaking at WIA_.[^wia]

For an example, see Tatiana Mac's [speaker rider](https://gist.github.com/tatianamac/493ca668ee7f7c07a5b282f6d9132552).


[^qi]: Among others. According to [Quote Investigator](https://quoteinvestigator.com/2014/03/01/short-speech/), the quote has been variably ascribed to several sources including Abraham Lincoln, Mark Twain, and William Howard Taft.

[^mayvary]: The amount of time needed certainly varies by whether or not you've "given this talk before" (I put quotes around that, as no two talks are truly the same).

[^erob]: There are enough posts extolling the virtues of public speaking that I wouldn't even know where to begin with a citation on this. Emily Robinson's ["Giving Your First Data Science Talk"](https://robinsones.github.io/Giving-Your-First-Data-Science-Talk/) is a nice resource.

[^wia]: I haven't been to this conference before, but I've heard only good things about it. Mai Alowaish wrote about [her experience last year](https://www.blastam.com/blog/women-in-analytics-2019-empowering-women-one-conference-at-a-time), which I enjoyed reading. There's also a press release for [WIA 2020](https://www.prweb.com/releases/women_in_analytics_announces_2020_conference_dates_and_keynote_speaker/prweb16421701.htm) with more detail.

